%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[6]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textbf{#3} & \textit{\small #4} \\
      {#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeEducation}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      {#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}



\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

% \renewcommand{\labelitemii}{$\circ$}
% \renewcommand{\labelitemi}{$\circ$}
\renewcommand{\labelitemii}{-}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}} r}
  \textbf{\href{https://veisec.github.io/resume_hlw/}{\Large Hsiao-Lun Wang}} & Email: \href{mailto:hsiaolunwang256@gmail.com}{hsiaolunwang256@gmail.com}\\
  \href{https://www.linkedin.com/in/hsiao-lun-wang} {LinkedIn}  \href{https://github.com/veisec} {GitHub}  & Mobile: \href{tel:+32 0492-80-22-82}{+32 492 80 22 82} \\
  
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeEducation
    {Ph.D. Degree in Electrical and Computer Engineering}{2020}
    {University of Illinois at Urbana-Champaign, Urbana, IL, USA}{}
    \resumeEducation
      {M.S. Degree in Photonics and Optoelectronics}{2013}
      {National Taiwan University, Taipei, Taiwan}{}
    \resumeEducation
    {B.S. Degree in Engineering Science}{2010}
    {National Taiwan University, Taipei, Taiwan}{}
  \resumeSubHeadingListEnd


% \section{Experiment}
% \begin{itemize}[leftmargin=*]
% \item[-]
%   \begin{tabular*}{\linewidth}[t]{l@{\extracolsep{\fill}}r}  % the [t] makes huge difference
%     {\textbf{University of Illinois at Urbana-Champaign}} & Urbana, IL, USA \\
%     \textit{\small Ph.D. degree in Electrical and Computer Engineering} & \textit{2020} \\
%   \end{tabular*}
% \item \textbf{PostDoc at imec 3DSIP}
% \end{itemize}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Postdoctoral Researcher }{Feb 2022 - Present}
      {imec - 3DSiP - Pathfinding}{Leuven, Belgium}
      {Hybrid Laser Integration with Silicon Photonics}{}
      \resumeItemListStart
        \resumeItem{PIC Design and Layout}
          {Using internal isipp200 PDK to layout and tapeout intergratged InP/Si(N) laser devices}
        \resumeItem{Laser Modeling}
          {Numerically solved laser rate equation using Matlab and Python. DFB laser frequency noise and RIN modeling}
        \resumeItemListEnd

    \resumeSubheading
      {Senior R\&D Engineer}{Sep 2020 - Oct 2021}
      {Lumentum - 3D Sensing}{San Jose, CA, USA}
      {Multi-Junction VCSEL Array}{}
      \resumeItemListStart
        \resumeItem{Chip design and testing coordination to meet product specs}
          {VCSEL array LIV, near-field and far-field data analysis}
        \resumeItem{Design and deliver 6-inch mass production chips to customers}
          {Provide updates on the qualification to external customers and internal R\&D team}
        \resumeItem{Tape-out test board for multi-junction VCSEL bandwidth characterization}
          {}
      \resumeItemListEnd

    \resumeSubheading
      {Doctoral Research and Teaching Assistant}{Aug 2015 - Aug 2020}
      {UIUC - HSIC}{Urbana, IL, USA}
      {Microwave High-Speed VCSEL}{}
      \resumeItemListStart
        \resumeItem{50Gb/s VCSEL at 850 nm}
          {}
        \resumeItem{Single-mode 50 Gb/s VCSEL}
          {}
        \resumeItem{Vertical-Cavity Transistor Laser}
        {Process DOE and establish process flow for three-terminal transistor laser
        - Improve oxidation control and demonstrate reliable micro-cavity process}
        \resumeItemListEnd

    \resumeSubheading
      {Hardware Intern}{May 2019 - Aug 2019}
      {Apple - PPO Engeering}{Cupertino, CA, USA}
      {Thin-Film Optical Characterization}{}
      \resumeItemListStart
        \resumeItem{RI and Thickness of Reflectors}
          {Conduct optical characterizations and analysis on thin-film samples}
        \resumeItemListEnd

  \resumeSubHeadingListEnd


% %-----------PROJECTS-----------------
% \section{Projects}
%   \resumeSubHeadingListStart
%     \resumeSubItem{QuantSoftware Toolkit}
%       {Open source python library for financial data analysis and machine learning for finance.}
%     \resumeSubItem{Github Visualization}
%       {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%     \resumeSubItem{Recommendation System}
%       {Music and Movie recommender systems using collaborative filtering on public datasets.}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
%   \resumeSubHeadingListEnd

%-----------Engineer Skills-----------------
\section{Engineer Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Chip Design and Layout}
      {Lumerical, IPKISS, GDStk}

    \resumeSubItem{Scripting Languages}
      {python, MATLAB, bash, Latex, JMP}

    \resumeSubItem{Device Modeling}
      {python and Matlab for laser rate equations}

    \resumeSubItem{VCSEL Fabrications}
      {lithography, nitride/oxide deposition (PECVD), Freon and chlorine based etching (ICP-
      RIE), metal deposition (E-beam), wet thermal oxidation (tube furnace), SEM}

    \resumeSubItem{Optical Characterization and Testing}
      {ellipsometer; thin-film reflectance and transmittance,LIV, spectrum, microwave optical bandwidth, s-parameters, link BERT}

  \resumeSubHeadingListEnd


% % --------Engineer SKILLS------------
% \section{Engineer Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------

\section{Publications}
\begin{enumerate}

\item A. Marinins et al., "Wafer-Scale Hybrid Integration of InP DFB Lasers on Si Photonics by Flip-Chip Bonding With sub-300 nm Alignment Precision," in IEEE JSTQE, vol. 29, no. 3, pp. 1-11, 2023.
\item J. Qiu, D. Wu, H. -L. Wang, M. Feng and X. Yu, "Advanced Single-Mode 850 nm VCSELs for Record NRZ and PAM4 Data Rate on SMF-28 Fiber up to 1 km," 2021 Optical Fiber Communications Conference and Exhibition (OFC), San Francisco, CA, USA, 2021, pp. 1-3.
\item H.L. Wang, J. Qiu, X. Yu, W. Fu and M. Feng, “The Modal Effect of VCSELs on Transmitting Data-Rate over Distance in OM4 Fiber”, IEEE J. Quantum Electron., vol. 56, no. 6, pp. 1–6, Dec. 2020.  
\item H. L. Wang, W. Fu, J. Qiu and M. Feng, “850 nm VCSELs for 50 Gb/s NRZ Error-Free Transmission over 100-meter OM4 and up to 115 oC Operation”, Optical Fiber Communication Conference and Exhibition (OFC), San Diego, USA (2019)   
\item H. L. Wang, J. Qiu, X. Yu, M. Feng and N. Holonyak, Jr., “85°C Operation of 850 nm VCSELs Deliver a 42 Gb/s Error-Free Data Transmission for 100 meter MMF Link”, Optical Fiber Communication Conference and Exhibition (OFC), San Diego, USA (2018)
\item J. Qiu, H. L. Wang, C. Wang, X. Yu and M. Feng, “40 Gb/s VCSELs Test Data Collection, Analysis and Process Problem Identification” 2017 CS MANTEEC, Indian Well, USA (2017) 
\item H. L. Wang, Y. H. Huang, G. S. Cheng, S. W. Chang, and C. H. Wu, “Analysis of Tunable Internal Loss Caused by Franz-Keldysh Absorption in Transistor Lasers”, IEEE J. Sel. Topics Quantum Electron, vol. 21, no. 6, 1503007 (2015)
\item H. H. Yang, W. C. Tu, H. L. Wang, and C. H. Wu, “Investigation of effective base transit time and current gain modulation of light-emitting transistors under different ambient temperatures”, Appl. Phys. Lett., vol. 105, 181119 (2014)
\item H. L. Wang, H. H. Yang, and C. H. Wu, “Quantum Well Saturation Effect on the Reduction of Base Transit Time in Light-Emitting Transistors”, IEEE Trans. Electron Devices, vol. 61, no. 10, pp. 3472-3476 (2014)
\item H. L. Wang, Y. J. Huang, and C. H. Wu, “Optical frequency response analysis of light-emitting transistors under different microwave configurations,” Appl. Phys. Lett., vol. 103, 051110 (2013)
\item Y. M. Liao, H. L. Wang, Yuh-Renn Wu, and C. H. Wu, “The dependence of base dynamics and current gain in the InGaAs/GaAs light emitting transistors,” ISCS/IPRM 2013, Kobe, Japan, 2013
\item H. L. Wang, P. H. Chou, and C. H. Wu, "Microwave determination of quantum-well capture and escape time in light-emitting transistors", IEEE Trans. Electron Devices, vol. 60, no. 3, pp. 1088-1091 (2013)
\item P. H. Chou, H. L. Wang, and C. H. Wu, “Comparison of Electrical and Optical f3dB Bandwidth in Light-Emitting Transistors,” OPTIC 2012, Taipei, Taiwan, 2012
\item P. H. Chou, H. L. Wang, and C. H. Wu, “The effect of aperture layout design on the multi-GHz operation of light-emitting transistors,” Proc. SPIE 8564, Nanophotonics and Micro/Nano Optics, 85640D, Beijing, China, 2012
  
\end{enumerate}


\end{document}